---
title: "Quarto Report: Health & Crime Analysis"
author: "Shiny AXI"
date: "June 17, 2026"
format:
  html:
    embed-resources: true
    theme: cosmo
    toc: true
---

# Introduction

This is an example Quarto document showcasing a summary table created using the `gtsummary` package and an interactive chart rendered using the `echarts4r` package.

## Demographic Summary

Below is a demographic summary table using the built-in `trial` dataset from `gtsummary`.

```{r}
#| label: summary-table
#| echo: false
#| message: false
#| warning: false
library(gtsummary)
library(dplyr)

tbl <- trial %>%
  select(trt, age, grade, response) %>%
  tbl_summary(
    by = trt,
    label = list(age ~ "Patient Age", grade ~ "Tumor Grade", response ~ "Tumor Response")
  ) %>%
  add_p()

# Insert blank rows before Tumor Grade and Tumor Response
blank_row_1 <- tbl$table_body[1, ]
blank_row_1[] <- lapply(blank_row_1, function(x) NA)
blank_row_1$variable <- "blank_space_1"
blank_row_1$row_type <- "label"
blank_row_1$label <- ""

blank_row_2 <- tbl$table_body[1, ]
blank_row_2[] <- lapply(blank_row_2, function(x) NA)
blank_row_2$variable <- "blank_space_2"
blank_row_2$row_type <- "label"
blank_row_2$label <- ""

tbl$table_body <- bind_rows(
  tbl$table_body[1:2, ],
  blank_row_1,
  tbl$table_body[3:6, ],
  blank_row_2,
  tbl$table_body[7:nrow(tbl$table_body), ]
)

tbl %>%
  as_gt() %>%
  gt::tab_header(title = "Table Header")
```

## Interactive Arrests Chart

Below is an interactive chart created using `echarts4r` displaying a subset of the US Arrests dataset.

```{r}
#| label: echart-plot
#| echo: false
#| message: false
#| warning: false
library(echarts4r)

USArrests %>%
  mutate(State = rownames(USArrests)) %>%
  e_charts(State) %>%
  e_bar(Assault, name = "Assault Rate") %>%
  e_line(Rape, name = "Rape Rate") %>%
  e_color(c("purple", "indigo")) %>%
  e_x_axis(axisLabel = list(interval = 0, rotate = 45)) %>%
  e_title("Crime Rates by State") %>%
  e_tooltip(trigger = "axis")
```
